Workflow Part II: Inverse root modeling and post-processing

### 2021-04-06 Readme.Rmd
rmarkdown, bookdown via groundhog

**Main text**
```{r Chunk 09.0, eval = FALSE}
# Two files are used within the report
# For data, 06.0_load.R and 
# For figures and data, code/08.0_manuscript_data_figs.R
if (!require("groundhog")) install.packages("groundhog"); 
groundhog.folder <- paste0("Users/ftuser/Library/R/4.0/library/bci.roots.inversion")
if(!dir.exists(file.path(groundhog.folder))) {dir.create(file.path(groundhog.folder))}
set.groundhog.folder(groundhog.folder)
library(groundhog)
groundhog.day = "2021-01-01"
# groundhog.library('rmarkdown', groundhog.day)
# .rs.restartR() to restart R session
groundhog.library('bookdown', groundhog.day)
groundhog.library('knitr', groundhog.day)
# rmarkdown::render("09.0_manuscript.rmd", output_format = "bookdown::html_document2")
render("09.0_manuscript.rmd", output_format = "bookdown::word_document2")
```

>>>>

**Main text**
```{r Chunk 09.0, eval = FALSE}
# Two files are used within the report
# For data, 06.0_load.R and 
# For figures and data, code/08.0_manuscript_data_figs.R
if (!require("groundhog")) install.packages("groundhog")
library(groundhog)
groundhog.folder <- paste0("Users/ftuser/Library/R/4.0/library/bci.roots.inversion")
if(!dir.exists(file.path(groundhog.folder))) {dir.create(file.path(groundhog.folder))}
set.groundhog.folder(groundhog.folder)

groundhog.day = "2021-01-01"
groundhog.library('rmarkdown', groundhog.day)
# .rs.restartR() to restart R session
groundhog.library('bookdown', groundhog.day)
# groundhog.library('knitr', groundhog.day)
# rmarkdown::render("09.0_manuscript.rmd", output_format = "bookdown::html_document2")
rmarkdown::render("09.0_manuscript.rmd", output_format = "bookdown::word_document2")
```
